Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-23 ICML2019/main.tex
Merge

\begin{thm}
  Algorithm \ref{mech:sexpmech} is $\epsilon$-d.p.
\end{thm}
% As already mentioned $\hexpmech$ extends straightforwardly to the Dirichlet-multinomial system.
% Indeed, the Hellinger distance between two Dirichlet distribution, unfolds in:
% \[
%   \hellinger(\dirichlet{\valpha_1}, \dirichlet{\valpha_2}) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
% \]
% and the $\candidateset$ will consist of the set of all possible posterior Dirichlet
% distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
% in (\ref{thm_gamma_smooth}) will be computed by letting $\dataobs'$ range
% over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. 
\section{Accuracy Analysis}

\subsection{Accuracy Bound for Baseline Mechanisms}

@@

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
\begin{lem}
\label{lem_acc_lap}
Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
\begin{align*}
&
\lapmechPr{\dataobs}{
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
}
\\
&\qquad = 
\begin{cases}
\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }}) &  t \geq 0\\
\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta }} - e^{\frac{\epsilon (t)}{\Delta }}) & t < 0
\end{cases}
\end{align*}
where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer{\dataobs} = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
\end{lem}
(Proof is in Appendix)

%  Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.\\  
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.\\
Instantiating $t$ with specific values ($0,1,2$ for example) and $\epsilon = 1$, we get the following accuracy equations on Laplace mechanism:
%\begin{align*}
%&\lapmechPr{\dataobs}{
%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0
%} = 0.19673467014,\\
%&\lapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
%\end{aligned}
%  } = 0.11932560927,\\
%&\lapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}
%  \end{aligned}
%} = 0.07237464051.
%\end{align*}
%In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
\begin{align*}
&\lapmechPr{\dataobs}{
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
}\\
& \qquad = \begin{cases}
0.19673467014 & t = 0\\
0.11932560927 & t = 1\\
0.07237464051 & t = 2
\end{cases}.
\end{align*}

\subsubsection{Accuracy Bound for Improved Laplace Mechanism}
\label{subsec_accuracy_lap}
Accuracy bound for improved Laplace mechanism is obtained from the standard Laplace Mechanism by replacing the sensitivity of $\Delta \bysinfer$ with $1$ in Beta-binomial model and $2$ in Dirichlet-multinomial model.

Given $t$ with the same specific values ($0,1,2$) and $\epsilon = 1$ as above, we get the following accuracy equations on improved Laplace mechanism:

\begin{align*}
&
\ilapmechPr{\dataobs}{
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
}
\\
&\qquad = 
\begin{cases}
\frac{1}{2} (e^{- \frac{\epsilon (t)}{2}} - e^{- \frac{\epsilon (t + 1)}{2}}) &  t \geq 0\\
\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{2}} - e^{\frac{\epsilon (t)}{2}}) & t < 0
\end{cases}
\end{align*}
%Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
%\begin{align*}
%&\ilapmechPr{\dataobs}{
%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}= 0.31606027941,\\
%&\ilapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
%  \end{aligned}
%} = 0.116272079,\\
%&\ilapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}} 
%    \end{aligned}
%} = 0.04277411.
%\end{align*}
%In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
\begin{align*}
&\ilapmechPr{\dataobs}{
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
}\\
& \qquad = \begin{cases}
0.31606027941 & t = 0\\
0.11627207896 & t = 1\\
0.04277410743 & t = 2
\end{cases}.
\end{align*}

\subsection{Accuracy Bound for $\hexpmech$}
\label{subsec_accuracy_smoo}
\begin{lem}
\label{lem_acc_hexp}
  In Beta-binomial model,
  we have following accuracy bound for this mechanism:
%  \begin{align*}
%  \label{eq_acc}
%  & \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  }\\ 
%  = & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
%  \end{align*}
%
%  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$
  \begin{align*}
  \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(t)  } }\\ 
  &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}\\
  & \text{ where } c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
  \end{align*}
\end{lem}

@@

% In the case when $\alpha = \beta$, there are always 2 symmetric beta distributions with the same distance from the true posterior, then we have accuracy table as:
% \begin{table*}[t]
% \scriptsize
% \centering
% \begin{tabular}{ |c|c|c|c|c| } 
% \hline
%  c & 0 
%  & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
%   & $1 - 
%     \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%     \cdot
%     \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$ & \dots  \\
%  \hline
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
%  & 0.19673467014 & 0.31606027941 & 0.19170024978 & \dots \\
%  \hline
%  $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
%  & 0.31606027941 & 0.43233235838 & 0.1590461864 & \dots \\
%  \hline
%  $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
%  & $\frac{1}{\nomalizer{\dataobs}}$ 
%  & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} 
%  \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ 
%  & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - 
%     \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%     \cdot
%     \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
%     {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ & \dots \\
%  \hline
% \end{tabular}
% \caption{Accuracy Comparison in Theoretical}
% \label{tab_acc_theo}
% \end{table*}

@@

By solving following equations:
%  \[
  %\frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
\begin{align*}
 &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(0)  } \\
 & = 0.19673467 \text{ or } 0.316060279
\end{align*}
%  \]
%  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the correct answer. 
%  \[
%  \frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
\begin{align*}
  &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(1)  }\\
  &= 0.119325609 \text{ or } 0.116272079
\end{align*}
%  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
%  \[
%\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
%    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%    \cdot
%    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
%    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
\begin{align*}
 &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(2)  }\\
 &=0.072374641 \text{ or }  0.042774107
%\]
\end{align*}
we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with two steps from the correct one... etc.

@@

% \subsection{Efficiency Evaluation}
% \label{subsec_effi}
% %The formula for computing the local sensitivity presented in Sec. \ref{sec_mechs}: %$LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
% %\[
% %LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
% %\]
% Thanks to the symmetry and triangle-inequality of the Hellinger
% distance, we can simplify the local sensitivity.
% \begin{lem}
% \[
% LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
% \]
% \end{lem}
% \begin{proof}
% For any $r \in \mathcal{R}$ and $\dataobs' \in \datauni^n$ with $\adj{\dataobs}{\dataobs'}$, we have
% \begin{align*}
% &\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
% & = 
% \begin{cases}
% \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
% \hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer(\dataobs), r) & \text{negative case}
% \end{cases}\\
% & \leq 
% \begin{cases}
% \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
% \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
% \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
% \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
% \end{cases}\\
% &= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
% \end{align*}
% The equality holds if $r = \bysinfer(\dataobs)$ or $r = \bysinfer(\dataobs')$.
% Hence, we conclude the statement of this lemma.
% \end{proof}

%In particular, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$.
%\begin{equation*}
%\begin{split}
%LS(\dataobs) 
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
%  & - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
%\end{split}
%\begin{align*}
%LS(\dataobs)
%& = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
%\left|~
%\begin{aligned}
%&\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs))\\
%&\quad - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
%\end{aligned}
%\right|\\
%  & = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
%\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs)).
%\end{align*}

>>>>

\begin{thm}
  Algorithm \ref{mech:sexpmech} is $\epsilon$-d.p.
\end{thm}
% As already mentioned $\hexpmech$ extends straightforwardly to the Dirichlet-multinomial system.
% Indeed, the Hellinger distance between two Dirichlet distribution, unfolds in:
% \[
%   \hellinger(\dirichlet{\valpha_1}, \dirichlet{\valpha_2}) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
% \]
% and the $\candidateset$ will consist of the set of all possible posterior Dirichlet
% distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
% in (\ref{thm_gamma_smooth}) will be computed by letting $\dataobs'$ range
% over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. 
\section{Accuracy Analysis}
We will observe accuracy of mechanisms.
In this section, we fix $\alpha$ and $\beta$, and for simplicity, we define the term of difference from $\betad(\alpha, \beta)$, the true posterior distribution.
\[
c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
\]
\subsection{Accuracy Bound for Baseline Mechanisms}

@@

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
\begin{lem}
\label{lem_acc_lap}
Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
\begin{align*}
&
\lapmechPr{\dataobs}{
\hellinger(\bysinfer{\dataobs}, z ) = c(t)
}
\\
&\qquad = 
\begin{cases}
\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }}) &  t \geq 0\\
\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta }} - e^{\frac{\epsilon (t)}{\Delta }}) & t < 0
\end{cases}
\end{align*}
where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer{\dataobs} = \betad(\alpha, \beta)$, and $z$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
\end{lem}
(Proof is in Appendix)

%  Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, r_L ) = 0} = 0.19673467014$.\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.\\  
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.\\
Instantiating $t$ with specific values ($0,1,2$ for example) and $\epsilon = 1$, we get the following accuracy equations on Laplace mechanism:
%\begin{align*}
%&\lapmechPr{\dataobs}{
%\textstyle\hellinger(\bysinfer{\dataobs}, r_L ) = 0
%} = 0.19673467014,\\
%&\lapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer{\dataobs}, r_L )^2 \\
%& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
%\end{aligned}
%  } = 0.11932560927,\\
%&\lapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer{\dataobs}, r_L )^2 \\
%& = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}
%  \end{aligned}
%} = 0.07237464051.
%\end{align*}
%In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
\[
\Pr[\hellinger(\bysinfer{\dataobs}, z ) = c(t)]
= \begin{cases}
0.19673467014 & t = 0\\
0.11932560927 & t = 1\\
0.07237464051 & t = 2
\end{cases}.
\]
%\begin{align*}
%&\ilapmechPr{\dataobs}{
%\hellinger(\bysinfer{\dataobs}, z ) = c(t)
%}\\
%& \qquad =  \begin{cases}
%0.31606027941 & t = 0\\
%0.11627207896 & t = 1\\
%0.04277410743 & t = 2
%\end{cases}.
%\end{align*}

\subsubsection{Accuracy Bound for Improved Laplace Mechanism}
\label{subsec_accuracy_lap}
Accuracy bound for improved Laplace mechanism is obtained from the standard Laplace Mechanism by replacing the sensitivity of $\Delta \bysinfer$ with $1$ in Beta-binomial model and $2$ in Dirichlet-multinomial model.
\begin{align*}
&
\ilapmechPr{\dataobs}{
\hellinger(\bysinfer{\dataobs}, z ) = c(t)
}
\\
&\qquad = 
\begin{cases}
\frac{1}{2} (e^{- \frac{\epsilon (t)}{2}} - e^{- \frac{\epsilon (t + 1)}{2}}) &  t \geq 0\\
\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{2}} - e^{\frac{\epsilon (t)}{2}}) & t < 0
\end{cases}
\end{align*}
%Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, r_L ) = 0} = 0.31606027941$.
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
%\begin{align*}
%&\ilapmechPr{\dataobs}{
%\textstyle\hellinger(\bysinfer{\dataobs}, r_L ) = 0}= 0.31606027941,\\
%&\ilapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer{\dataobs}, r_L )^2 \\
%& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
%  \end{aligned}
%} = 0.116272079,\\
%&\ilapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer{\dataobs}, r_L )^2 \\
%& = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}} 
%    \end{aligned}
%} = 0.04277411.
%\end{align*}
%In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

Given $t$ with the same specific values ($0,1,2$) and $\epsilon = 1$ as above, we get the following accuracy equations on improved Laplace mechanism:
\[
\Pr[
\hellinger(\bysinfer{\dataobs}, z ) = c(t)
]
 =  \begin{cases}
0.31606027941 & t = 0\\
0.11627207896 & t = 1\\
0.04277410743 & t = 2
\end{cases}.
\]
%\begin{align*}
%&\ilapmechPr{\dataobs}{
%\hellinger(\bysinfer{\dataobs}, z ) = c(t)
%}\\
%& \qquad =  \begin{cases}
%0.31606027941 & t = 0\\
%0.11627207896 & t = 1\\
%0.04277410743 & t = 2
%\end{cases}.
%\end{align*}

\subsection{Accuracy Bound for $\hexpmech$}
\label{subsec_accuracy_smoo}
\begin{lem}
\label{lem_acc_hexp}
  In Beta-binomial model,
  we have following accuracy bound for this mechanism:
%  \begin{align*}
%  \label{eq_acc}
%  & \hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c  }\\ 
%  = & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
%  \end{align*}
%
%  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$
  \begin{align*}
  \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c(t)  } }\\ 
  &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
%  & \text{ where } c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
  \end{align*}
\end{lem}

@@

% In the case when $\alpha = \beta$, there are always 2 symmetric beta distributions with the same distance from the true posterior, then we have accuracy table as:
% \begin{table*}[t]
% \scriptsize
% \centering
% \begin{tabular}{ |c|c|c|c|c| } 
% \hline
%  c & 0 
%  & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
%   & $1 - 
%     \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%     \cdot
%     \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$ & \dots  \\
%  \hline
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z ) = c} $
%  & 0.19673467014 & 0.31606027941 & 0.19170024978 & \dots \\
%  \hline
%  $\ilapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c}$
%  & 0.31606027941 & 0.43233235838 & 0.1590461864 & \dots \\
%  \hline
%  $\hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c}$
%  & $\frac{1}{\nomalizer{\dataobs}}$ 
%  & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} 
%  \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ 
%  & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - 
%     \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%     \cdot
%     \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
%     {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ & \dots \\
%  \hline
% \end{tabular}
% \caption{Accuracy Comparison in Theoretical}
% \label{tab_acc_theo}
% \end{table*}

@@

By solving equations on accuracy such as:
\begin{align*}
\lefteqn{\hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c(1)  }}\\
&\qquad =
\lapmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c(1)  }
=
0.19673467 
\end{align*}
%By solving following equations:
%  \[
%  %\frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
%\begin{align*}
% &\hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c(0)  } \\
% & = 0.19673467 \text{ or } 0.316060279
%\end{align*}
%  \]
%  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the correct answer. 
%  \[
%  \frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
%\begin{align*}
%  &\hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c(1)  }\\
%  &= 0.119325609 \text{ or } 0.116272079
%\end{align*}
%  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
%  \[
%\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
%    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%    \cdot
%    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
%    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
%\begin{align*}
% &\hexpmechPr{\dataobs}{\hellinger(\bysinfer{\dataobs}, z) = c(2)  }\\
% &=0.072374641 \text{ or }  0.042774107
%\]
%\end{align*}
we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with two steps from the correct one... etc.

@@

% \subsection{Efficiency Evaluation}
% \label{subsec_effi}
% %The formula for computing the local sensitivity presented in Sec. \ref{sec_mechs}: %$LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
% %\[
% %LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
% %\]
% Thanks to the symmetry and triangle-inequality of the Hellinger
% distance, we can simplify the local sensitivity.
% \begin{lem}
% \[
% LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer{\dataobs}, \bysinfer(\dataobs')).
% \]
% \end{lem}
% \begin{proof}
% For any $r \in \mathcal{R}$ and $\dataobs' \in \datauni^n$ with $\adj{\dataobs}{\dataobs'}$, we have
% \begin{align*}
% &\lvert \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
% & = 
% \begin{cases}
% \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
% \hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer{\dataobs}, r) & \text{negative case}
% \end{cases}\\
% & \leq 
% \begin{cases}
% \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})+
% \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
% \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})+
% \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer{\dataobs}, r)&
% \end{cases}\\
% &= \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})
% \end{align*}
% The equality holds if $r = \bysinfer{\dataobs}$ or $r = \bysinfer(\dataobs')$.
% Hence, we conclude the statement of this lemma.
% \end{proof}

%In particular, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer{\dataobs}$.
%\begin{equation*}
%\begin{split}
%LS(\dataobs) 
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer{\dataobs}, \bysinfer{\dataobs}) \\
%  & - \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})|\} \\
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})|\}.
%\end{split}
%\begin{align*}
%LS(\dataobs)
%& = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
%\left|~
%\begin{aligned}
%&\hellinger(\bysinfer{\dataobs}, \bysinfer{\dataobs})\\
%&\quad - \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})
%\end{aligned}
%\right|\\
%  & = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
%\hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs}).
%\end{align*}
